Replication analysis

### 2020-02-16 replication_analysis.Rmd
adding notes

# plot the grid
#ggpairs(lances_M[c(5,6,7,8,9,10,11)])
ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = "points", mapping = aes(color = site)),
        lower=list(continuous = "cor"),
        ggsave("Images/replication_fig_8.png"))
```

>>>>

# plot the grid
#ggpairs(lances_M[c(5,6,7,8,9,10,11)])
ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = "points", mapping = aes(color = site)),
        lower=list(continuous = "cor"),
        ggsave("Images/replication_fig_8.png"))

#notes for those who follow:
# check variable names - dont think sock_bdiam etc. is the same as min max width
# histogram as well as density on middle plots
# color match
# label match
```
